---
title: "p8105_hw5_km3529"
author: "Karina Myers"
date: "11/10/2020"
output: html_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_df = 
  read_csv("data/homicide/homicide.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"), 
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved", 
      disposition == "Open/No arrest" ~ "unsolved", 
      disposition == "Closed by arrest" ~ "solved"
    ) ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

DESCRIBE RAW DATA
  - Tulsla_AL had 1 obs, so removed s



Summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(), 
    hom_unsolved = sum(resolved == "unsolved")
  )
```


For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
prop.test(
  aggregate_df %>% filter(city_state ==  "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state ==  "Baltimore_MD") %>% pull(hom_total)) %>%
  broom::tidy()
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city. 
```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)), 
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)
```


Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state,  y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

* Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

* Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe


```{r}
path_df = 
  tibble(
    path = list.files("data/lda")
  ) %>% 
  mutate(
      path = str_c("data/lda/", path), 
      data = map(path, read_csv )) 
```


* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
lda_df = 
  path_df %>% 
  separate(path, into = c('folder', 'lda', 'id'), sep = "/") %>% 
  select(-folder, -lda) %>% 
  mutate(
    id = str_replace(id, '.csv' , '')) %>% 
  separate(id, into = c('arm', 'id'), sep = "_") %>% 
  unnest(col = data) %>% 
  pivot_longer(
    week_1:week_8, 
    names_to = "week",  
    values_to = "observation", 
    names_prefix = "week_"
  ) %>% 
  mutate(
    week = as.numeric(week))


## add this
mutate(

col name = str_replace(string, pattern, replacement)

)


```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
# doesn't work 
lda_df %>% 
  group_by(arm, id, week) %>% 
  summarize(observation) %>% 
  ggplot(aes(x = week, y = observation, color = arm)) + 
  geom_line() +
  labs(x = 'Week', 
       y = 'Observation Value', 
       title = 'Observations Over Time')

#trial 
lda_df %>% 
  group_by(arm, id) %>% 
  summarize(observation, week) %>% 
  ggplot(aes(x = week, y = observation, color = arm)) + 
  geom_line() +
  labs(x = 'Week', 
       y = 'Observation Value', 
       title = 'Observations Over Time')



lda_df %>% 
  ggplot(aes(x = week, y = observation, group = interaction(arm, id), color = arm)) + 
  geom_line() +
    labs(x = 'Week', 
      y = 'Observation Value', 
      title = 'Observations Over Time', 
      color = 'Treatment Group') 
 
```

COMMENT


## Problem 3


1) create a function that shows t test output 


```{r}
sim_ttest = function(mu){
  
  sim_data = 
    tibble(
      x = rnorm(n = 30, mean = mu, sd = 5)) 
  
  sim_data %>% 
    t.test(mu = 0, alternative = "two.sided", paired = FALSE, conf.level = 0.95) %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
  
}

sim_ttest(6)
sim_ttest(0)

```

Set mu = 0 and generate 5000 datasets 
```{r}
sim_results = 
  rerun(50, sim_ttest(0)) %>% 
  bind_rows() 
```

Repeat for mu = {1, 2, 3, 4, 5, 6} 
```{r}
sim_results2 = 
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = mu, ~rerun(5000, sim_ttest(mu = .x))), 
    estimate_df = map(output_lists, bind_rows)) %>% 
    unnest(estimate_df) %>% 
    select(-output_lists)
  
```


 
 
 
 
 
 
 
 
 
 
```{r}

sim_ttest = function(samp_size, mu, sigma) {
  
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma))

  sim_data %>% 
    t.test(mu = 0, alternative = "two.sided", paired = FALSE, conf.level = 0.95) %>% 
    broom::tidy() %>% 
  select(estimate, p.value)

} 

sim_ttest(30, 0, 6)

```

  


















